---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# hello

<!-- badges: start -->
<!-- badges: end -->

A set of functions to be polite with our colleagues and friends.

## Installation

You can install the development version of hello like so:

``` r
remotes::install_github("statnmap/hello")
remotes::install_gitlab("statnmap/hello")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(hello)
## basic example code
```


# Say hello to someone

You can say hello to someone in particular using `say_hello()`.


```{r examples-say_hello}
say_hello() # Hello Berra
say_hello(someone = "Seb") # Hello Seb

hello_anna <- say_hello(someone = "Anna") 
hello_anna
# library(ggplot2)
# ggplot() + geom_point()
```

## Code of Conduct
  
Please note that the hello project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
  
